Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-06-06 paper/background.tex
Revision about the citations
Paper revision

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
most commonly used model for Bayesian optimization. The advantage of GP is that
it provides a well-calibrated uncertainty of prediction. GP is characterized by
a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
this work, we use squared-exponential ARD kernel~\cite{GPML}, and a constant
mean function $m(\bm{x}) = \mu_0$ for all our experiments. By default, we
assume the objective function evaluations are influenced by i.i.d. noise
$\epsilon_t \sim N(0, \sigma_n^2)$ and set the noise level $\sigma_n^2$ as a
hyperparameter.  The introduction of the i.i.d noise also helps to improve the

@@

Following the suggestion of~\cite{brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
\begin{equation}
    \label{eq:LCBKappa}
    \begin{array}{lll}
        \kappa &=& \sqrt{\nu \tau_t} \\
        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta),
    \end{array}
\end{equation}
where $t$ is the number of current iteration, $\nu$ and $\delta$ are two user-defined parameters. We fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.

>>>>

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
most commonly used model for Bayesian optimization. The advantage of GP is that
it provides a well-calibrated uncertainty of prediction. GP is characterized by
a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
this work, we use squared-exponential ARD kernel~\cite{GPML}, and a constant
mean function $m(\bm{x}) = \mu_0$ for all our experiments. By default, we
assume the objective function evaluations are influenced by i.i.d. noise
$\epsilon_t \sim N(0, \sigma_n^2)$ and set the noise level $\sigma_n^2$ as a
hyperparameter.  The introduction of the i.i.d noise also helps to improve the numerical stability.

@@

Following the suggestion of~\cite{srinivas2010gaussian, brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
\begin{equation}
    \label{eq:LCBKappa}
    \begin{array}{lll}
        \kappa &=& \sqrt{\nu \tau_t} \\
        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta),
    \end{array}
\end{equation}
where $t$ is the number of current iteration, $\nu$ and $\delta$ are two user-defined parameters. We fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.

### 2018-06-06 paper/experiments.tex
Paper revision

The proposed MACE algorithm\footnote{Available at https://github.com/Alaya-in-Matrix/MACE} was tested using eight benchmark functions and two
real-world analog circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB
algorithm~\cite{desautels2014parallelizing}, the local penalization method with
EI acquisition function (EI-LP)~\cite{gonzalez2016batch}, the qEI and qKG
methods~\cite{qEI,wu2016parallel}. \footnote{We implemented the BLCB algorithm as
the available open source implementations only allow discrete input. For the
EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
from https://github.com/wujian16/Cornell-MOE}

@@

The mean convergence plots of the tested algorithms on the benchmark functions are
given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE.

\begin{table*}[!htb]
    \centering
    \caption{Optimization results of the benchmark functions}
    \label{tab:result_analytical}
    \begin{tabular}{lllllllllll}
        \toprule
                & Eggholder                &  Branin              &  Alpine1              & Hartmann6                   \\ \midrule
        MACE-1  & 87.65$\pm$75.83          &  1.05e-5$\pm$1.31e-5          & 2.66305$\pm$1.05844            & 0.0646869$\pm$0.0621189 \\
        LCB-1   & 153.9$\pm$112.8          &  6.86e-5$\pm$1.13e-4          & 5.66812$\pm$1.76973            & 0.125565$\pm$0.122684   \\
        EI-1    & 172.8$\pm$132.2          &  1.62e-2$\pm$1.63e-2          & 2.46061$\pm$1.56079            & 0.110561$\pm$0.146809   \\
        MACE-4  & 46.38$\pm$40.89          &  \textbf{4.62e-6$\pm$6.64e-6} & \textbf{0.903805$\pm$0.835209} & \textbf{0.0275738$\pm$0.052254}  \\
        BLCB-4  & 56.86$\pm$35.91          &  4.32e-5$\pm$6.33e-5          & 1.8843$\pm$0.938873            & 0.06447$\pm$0.0621176   \\
        EI-LP-4 & \textbf{44.68$\pm$56.45} &  2.11e-2$\pm$1.84e-2          & 1.0059$\pm$0.456865            & 0.0540446$\pm$0.0558557 \\
        qKG-4   & 106.4$\pm$67.64          &  2.65e-1$\pm$2.70e-1          & 3.01513$\pm$1.13414            & 0.47134$\pm$0.18939     \\
        qEI-4   & 72.13$\pm$52.08          &  3.29e-4$\pm$1.14e-3          & 2.7074$\pm$1.05145             & 0.186088$\pm$0.116323   \\
        \hline
                & Ackley2                       &  Rosenbrock2               & Ackley10              & Rosenbrock10        \\ \midrule
        MACE-1  & 1.71474$\pm$1.12154           &  0.026173$\pm$0.051189              & 3.1348$\pm$0.447874           & 499.697$\pm$300.899 \\
        LCB-1   & 1.624$\pm$0.926437            &  0.0201124$\pm$0.0205367            & 3.14797$\pm$0.519164          & 517.944$\pm$288.955 \\
        EI-1    & 1.0136$\pm$0.985858           &  13.5508$\pm$9.52734                & 18.8006$\pm$0.652136          & 1367.08$\pm$637.507 \\
        MACE-4  & 1.07906$\pm$0.886466          &  \textbf{0.00095416$\pm$0.00093729} & \textbf{2.56439$\pm$0.535488} & \textbf{158.116$\pm$50.0024} \\
        BLCB-4  & 1.40051$\pm$1.02849           &  0.00191986$\pm$0.00180895          & 3.27543$\pm$0.735501          & 406.819$\pm$127.351 \\
        EI-LP-4 & \textbf{0.284265$\pm$0.24634} &  2.73645$\pm$2.05923                & 18.2682$\pm$0.608564          & 721.351$\pm$327.365 \\
        qKG-4   & 5.59394$\pm$1.80595           &  5.03976$\pm$3.72014                & 18.197$\pm$0.764103           & 705.112$\pm$412.762 \\
        qEI-4   & 2.87373$\pm$1.02405           &  10.1881$\pm$15.0432                & 18.3686$\pm$0.501869          & 655.208$\pm$340.954 \\
        \bottomrule
    \end{tabular}
\end{table*}

>>>>

The proposed MACE algorithm\footnote{Available at https://github.com/Alaya-in-Matrix/MACE} was tested using eight benchmark functions and two
real-world analog circuits. Four state-of-the-art parallel Bayesian optimization
methods were compared, including the BLCB
algorithm~\cite{desautels2014parallelizing}, the local penalization method with
EI acquisition function (EI-LP)~\cite{gonzalez2016batch}, the qEI and qKG
methods~\cite{qEI,wu2016parallel}. \footnote{We implemented the BLCB algorithm as
the available open source implementations only allow discrete input. For the
EI-LP method, the code is downloaded from
https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
from https://github.com/wujian16/Cornell-MOE.}

@@

The mean convergence plots of the tested algorithms on the benchmark functions
are given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
regrets are listed in Table~\ref{tab:result_analytical}. As can be seen in
Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when
running in sequential mode, the MACE algorithm is competitive with the LCB and
EI acquisition functions. The sequential MACE (MACE-1) algorithm gave better
performances than the sequential EI (EI-1) and sequential LCB (LCB-1)
algorithms in the Eggholder, Branin, Hartmann6, Ackley10, and Rosenbrock10
functions. Also, the parallel MACE (MACE-4) gave the best performances among
all the tested algorithms for six out of the eight benchmark functions, and has
shown dramatic speedup compared to the sequential MACE. We also performed
additional experiments with varied batch sizes, the detail of those
experimental results can be seen in the supplementary materials.

\begin{table*}[!htb]
    \centering
    \caption{Statistics of the regrets of the benchmark functions}
    \label{tab:result_analytical}
    \begin{tabular}{lllllllllll}
        \toprule
                & Eggholder                &  Branin              &  Alpine1              & Hartmann6                   \\ \midrule
        MACE-1  & 87.65$\pm$75.83          &  1.05e-5$\pm$1.31e-5          & 2.66305$\pm$1.05844            & 0.0646869$\pm$0.0621189 \\
        LCB-1   & 153.9$\pm$112.8          &  6.86e-5$\pm$1.13e-4          & 5.66812$\pm$1.76973            & 0.125565$\pm$0.122684   \\
        EI-1    & 172.8$\pm$132.2          &  1.62e-2$\pm$1.63e-2          & 2.46061$\pm$1.56079            & 0.110561$\pm$0.146809   \\
        MACE-4  & 46.38$\pm$40.89          &  \textbf{4.62e-6$\pm$6.64e-6} & \textbf{0.903805$\pm$0.835209} & \textbf{0.0275738$\pm$0.052254}  \\
        BLCB-4  & 56.86$\pm$35.91          &  4.32e-5$\pm$6.33e-5          & 1.8843$\pm$0.938873            & 0.06447$\pm$0.0621176   \\
        EI-LP-4 & \textbf{44.68$\pm$56.45} &  2.11e-2$\pm$1.84e-2          & 1.0059$\pm$0.456865            & 0.0540446$\pm$0.0558557 \\
        qKG-4   & 106.4$\pm$67.64          &  2.65e-1$\pm$2.70e-1          & 3.01513$\pm$1.13414            & 0.47134$\pm$0.18939     \\
        qEI-4   & 72.13$\pm$52.08          &  3.29e-4$\pm$1.14e-3          & 2.7074$\pm$1.05145             & 0.186088$\pm$0.116323   \\
        \hline
                & Ackley2                       &  Rosenbrock2               & Ackley10              & Rosenbrock10        \\ \midrule
        MACE-1  & 1.71474$\pm$1.12154           &  0.026173$\pm$0.051189              & 3.1348$\pm$0.447874           & 499.697$\pm$300.899 \\
        LCB-1   & 1.624$\pm$0.926437            &  0.0201124$\pm$0.0205367            & 3.14797$\pm$0.519164          & 517.944$\pm$288.955 \\
        EI-1    & 1.0136$\pm$0.985858           &  13.5508$\pm$9.52734                & 18.8006$\pm$0.652136          & 1367.08$\pm$637.507 \\
        MACE-4  & 1.07906$\pm$0.886466          &  \textbf{0.00095416$\pm$0.00093729} & \textbf{2.56439$\pm$0.535488} & \textbf{158.116$\pm$50.0024} \\
        BLCB-4  & 1.40051$\pm$1.02849           &  0.00191986$\pm$0.00180895          & 3.27543$\pm$0.735501          & 406.819$\pm$127.351 \\
        EI-LP-4 & \textbf{0.284265$\pm$0.24634} &  2.73645$\pm$2.05923                & 18.2682$\pm$0.608564          & 721.351$\pm$327.365 \\
        qKG-4   & 5.59394$\pm$1.80595           &  5.03976$\pm$3.72014                & 18.197$\pm$0.764103           & 705.112$\pm$412.762 \\
        qEI-4   & 2.87373$\pm$1.02405           &  10.1881$\pm$15.0432                & 18.3686$\pm$0.501869          & 655.208$\pm$340.954 \\
        \bottomrule
    \end{tabular}
\end{table*}

### 2018-06-06 paper/mace.tex
Paper revision

Each acquisition function represents a unique selection strategy, different acquisition functions may not agree with each other about where to sample the next point. For example, the value of LCB function always decreases as the $\sigma(\bm{x})$ increases. However, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$. For the EI function, the values of EI function at already sampled points would always be lower than the values at any unsampled locations, while this property does not hold for the LCB function.

>>>>

Each acquisition function represents a unique selection strategy, different acquisition functions may not agree with each other about where to sample the next point. For example, the value of LCB function always decreases as the $\sigma(\bm{x})$ increases. However, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$. For the EI function, if the function is noiseless, the values of EI function at already sampled points would always be worse than the EI values at any unsampled locations, while this property does not hold for the LCB function.
